---
title: "rbtl-fs25 end-of-semester exam"
subtitle: "Section 03"
format:
  html:
    embed-resources: true
editor: visual
execute: 
  echo: true
  warning: false
editor_options: 
  chunk_output_type: console
---

# Points

The maximum number of points for this section is: **13 out of 53**. The number of points for each task is shown in parenthesis next to the task number.

# Task 3.1 (0.5)

1.  Render the document and fix any errors.

```{r}
library(tidyverse)
```

You will work with the `generation` and `treatment_long` data objects.

```{r}
generation <- read_csv("data/what-a-waste/waste-generation.csv")
treatment_long <- read_csv("data/what-a-waste/treatment-long.csv")
```

# Task 3.2 (1)

The following code performs a join operation to combine the `treatment_long` and `generation` data objects based on the common columns `country`, `city`, and `income_id`. The result is stored in a new data object called `treatment_generation`.

1. Run the code below to perform the join operation.

2. Explore the resulting `treatment_generation` data object and think about the content of the `value` column.

```{r}

treatment_generation <- treatment_long |> 
  left_join(generation, by = c("country", "city", "income_id"))

```

# Task 3.3 (8)

This task requires you to analyze waste treatment data through multiple steps. You may create intermediate data objects if needed.

## Background Information

The `value` column in the `treatment_generation` data represents the percentage of waste that receives each treatment type. This percentage applies proportionally to both the waste generation AND the population figures.

## Your Task: Answer Three Questions

**Step 1: Data Preparation** First, create a comprehensive dataset that:

-   Calculates actual tons of waste for each treatment type (using percentages from `value` column in combination with `waste_generation`)

-   Adjusts population figures proportionally to match the treatment percentages

-   Groups data by country and treatment type

-   Summarizes total waste and population for each country-treatment combination

-   Calculate per capita waste generation in kg/day

**Question 1:** Using your prepared data, determine how many tons of waste per year are openly dumped in Sri Lanka and Bhutan combined.


```{r}


```

# Task 3.4 - Hand-in (0.5)

1.  Render the document and fix any errors.

Last complete render: `r Sys.time()` at timezone `r Sys.timezone()`.
