---
title: "rbtl-fs25 end-of-semester exam"
subtitle: "Section 02"
format:
  html:
    embed-resources: true
editor: visual
execute: 
  echo: true
  warning: false
editor_options: 
  chunk_output_type: console
---

# Points

The maximum number of points for this section is: **9 out of 53**. The number of points for each task is shown in parenthesis next to the task number.

# Task 2.0 (0.5)

1.  Render the document and fix any errors.

```{r}
library(tidyverse)
```

```{r}
treatment <- read_csv("data/what-a-waste/waste-treatment.csv")
```

# Task 2.1 (0.5)

1.  Explore the treatment data object using functions taught during the course.

```{r}

```

# Task 2.2 (2)

The `treatment` data does not follow tidy data principles. It is in a wide format rather than in a long format and shows different types of waste treatment in different columns, which could be one column with the type of treatment and another column with the value of the treatment.

1.  Use functions taught in the course to create a new object that follows tidy data principles.

2.  Remove NAs from the data and keep only treatment values greater than 0.

3.  Store the result as a new object in your environment with the name `treatment_tidy`.

```{r}

```

# Task 2.3 (1)

1.  Starting with the `treatment_tidy` data object, use functions taught during the course to answer the following question:

How many countries are covered in this dataset?

```{r}

```

# Task 2.4 (1.5)

1.  Starting with the `treatment_tidy` data object, use functions taught during the course to answer the following question:

Which country has the highest number of cities in the dataset, and how many cities is that?

```{r}


```

# Task 2.5 (3)

1.  Starting with the `treatment_tidy` data object, use functions taught during the course to answer the following questions:

-   How many categories of waste treatment are there in the dataset?
-   How many categories are related to landfill? (Requirement: use `str_detect()` to identify them)
-   In how many cities is at least 50% of waste sent to a controlled landfill?

```{r}

```

# Task 2.6 - Hand-in (0.5)

1.  Render the document and fix any errors.

Last complete render: `r Sys.time()` at timezone `r Sys.timezone()`.
